Articles of Association of London Hackspace Ltd

### 2014-11-16 constitution/articles-body.tex
Correct duplicated clause 38.c.iii
Corrected form is from earlier drafts of the articles.
Make clear that membership requires a valid email address
Fix election/re-election confusion
Remove duplicate directors retirement clause

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the association.
  \item
    Membership is open to other individuals or organisations who:
    \begin{enumerate}
    \item
      apply to the association in the form required by the directors; and
    \item
      are approved by the directors.
    \end{enumerate}
  \item

@@

\item
  \begin{enumerate}
  \item
    The directors to retire by rotation shall be those who have been
    longest in office since their last appointment. If any directors
    became or were appointed directors on the same day those to retire
    shall (unless they otherwise agree among themselves) be determined
    by lot.
  \item
    If a director is required to retire at an annual general meeting by
    a provision of the articles the retirement shall take effect upon
    the conclusion of the meeting.
  \end{enumerate}

@@

\item
  No person other than a director retiring by rotation may be
  appointed a director at any general meeting unless:
  \begin{enumerate}
  \item
    he or she is recommended for re-election by the directors; or
  \item
    not less than fourteen nor more than thirty-five clear days before
    the date of the meeting, the association is given a notice that:
    \begin{enumerate}
    \item
      is signed by a member entitled to vote at the meeting;
    \item
      states the member's intention to propose the appointment of a
      person as a director;
    \item
      contains the details that, if the person were to be appointed, the
      association would have to file at Companies House; and
    \item
      is signed by the person who is to be proposed to show his or her
      willingness to be appointed.
    \end{enumerate}
  \end{enumerate}
\item
  All members who are entitled to receive notice of a general meeting
  must be given not less than seven nor more than twenty-eight clear
  days' notice of any resolution to be put to the meeting to appoint
  a director other than a director who is to retire by rotation.

@@

\item
    \begin{enumerate}
    \item
        The directors may delegate any of their powers or functions concerning the day
        to day management of the affairs of the Company to any person or persons as they may
        from time to time select.
    \item
        All acts done by a director shall, even if it is afterwards discovered that there was
        a defect in their appointment or that they were disqualified from holding office or had
        vacated office, be as valid as if such person had been duly appointed and was qualified
        and had continued to be a director.
    \item
        Where on any particular occasion more than 2 directors, in the course of their
        office as directors, discuss the affairs of the Company by any means, whether in person
        or otherwise, a minute shall be made and recorded indicating:
            \begin{enumerate}
                \item
                    when the discussion took place;
                \item
                    the identities of the directors involved; and
                \item
                    the identities of the directors involved; and
            \end{enumerate}
    \item
        Minutes of directors meetings:
            \begin{enumerate}
                \item
                    may be held in electronic form, and in particular using the Governance System;
                \item
                    must be held for ten years from the date of the discussion in accordance with section
                    248 of the Companies Act 2006.
            \end{enumerate}
    \end{enumerate}

>>>>

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the association.
  \item
    Membership is open to other individuals or organisations who:
    \begin{enumerate}
    \item
      apply to the association in the form required by the directors;
    \item
      supply a valid e-mail address; and
    \item
      are approved by the directors
    \end{enumerate}
  \item

@@

@@

\item
  No person other than a director retiring by rotation may be
  appointed a director at any general meeting unless:
  \begin{enumerate}
  \item
    he or she is recommended for election by the directors; or
  \item
    not less than fourteen nor more than thirty-five clear days before
    the date of the meeting, the association is given a notice that:
    \begin{enumerate}
    \item
      is signed by a member entitled to vote at the meeting;
    \item
      states the member's intention to propose the appointment of a
      person as a director;
    \item
      contains the details that, if the person were to be appointed, the
      association would have to file at Companies House; and
    \item
      is signed by the person who is to be proposed to show his or her
      willingness to be appointed.
    \end{enumerate}
  \end{enumerate}
\item
  All members who are entitled to receive notice of a general meeting
  must be given not less than seven nor more than twenty-eight clear
  days' notice of any resolution to be put to the meeting to appoint
  a director other than a director who is to retire by rotation.

@@

\item
    \begin{enumerate}
    \item
        The directors may delegate any of their powers or functions concerning the day
        to day management of the affairs of the Company to any person or persons as they may
        from time to time select.
    \item
        All acts done by a director shall, even if it is afterwards discovered that there was
        a defect in their appointment or that they were disqualified from holding office or had
        vacated office, be as valid as if such person had been duly appointed and was qualified
        and had continued to be a director.
    \item
        Where on any particular occasion more than 2 directors, in the course of their
        office as directors, discuss the affairs of the Company by any means, whether in person
        or otherwise, a minute shall be made and recorded indicating:
            \begin{enumerate}
                \item
                    when the discussion took place;
                \item
                    the identities of the directors involved; and
                \item
                    the substance of the discussion.
            \end{enumerate}
    \item
        Minutes of directors meetings:
            \begin{enumerate}
                \item
                    may be held in electronic form, and in particular using the Governance System;
                \item
                    must be held for ten years from the date of the discussion in accordance with section
                    248 of the Companies Act 2006.
            \end{enumerate}
    \end{enumerate}
